Syntax and Semantics of Abstract Binding Trees

### 2015-11-10 paper.tex
[paper] annotate the Grothendieck opfibration
Switch back to pdflatex

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{agda} % this should come after ams*
\usepackage{catchfilebetweentags}
\usepackage{fontspec}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{ifdraft}
\usepackage{ifthen}
\usepackage{lualatex-math}
%\usepackage{mathtools}
\usepackage{proof}
\usepackage{scalerel}
\usepackage{setspace}
\usepackage{stmaryrd}
\usepackage{supertabular}
\usepackage{tikz-cd}
\usepackage{unicode-math}
\usepackage{url}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{xunicode}

@@

% fonts
\usepackage[
  activate={true,nocompatibility},
  tracking=true
]{microtype}
\setmainfont{Linux Libertine O}
\setmathfont{Asana Math}

@@

Then, fix a covariant presheaf (copresheaf) of operators
$\Of{\Operators}{\SCtx\times\Discrete{\Arities}\to\Sets}$ such that the arrows
in $\SCtx$ lift to renamings of operators' parameters. By the Grothendieck
construction $\Iso{\Grothendieck{}{\Operators}}{\Comma{𝟙}{\Operators}}$ we have
a category of elements of $\Operators$ where objects are triples
$\Pair{\Pair{\Upsilon}{a}}{\vartheta}$, interpreted as
$\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$, and morphisms are diagrams:

\[
  \begin{tikzcd}[ampersand replacement = \&]
    \& 𝟙
      \arrow[dl, "\vartheta", swap]
      \arrow[dr, "\vartheta'"]
    \&
    \\
    {\Operators\Pair{\Upsilon}{a}}
      \arrow[rr, "\Operators\Pair{\rho}{f}", swap]
    \&
    \& {\Operators\Pair{\Upsilon'}{a'}}
    \\
    {\Pair{\Upsilon}{a}}
      \arrow[rr, "\Pair{\rho}{f}", swap]
    \&
    \& {\Pair{\Upsilon'}{a'}}
  \end{tikzcd}
\]\\

@@

Operators are defined by specifying the fibers of $\pi_{\Operators}$ in which
they reside. For instance, consider the lambda calculus with a single sort,
$\SortExp$; we give its signature by asserting the following about its
operators:
\begin{gather*}
  \IsOperator{\Upsilon}{\lambda}{
    \MkArity{\MkValence{}{\SortExp}{\SortExp}}{\SortExp}
  }\\
  \IsOperator{\Upsilon}{\mathsf{ap}}{
    \MkArity{
      \MkValence{}{}{\SortExp},
      \MkValence{}{}{\SortExp}
    }{\SortExp}
  }
\end{gather*}

>>>>

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{agda} % this should come after ams*
\usepackage{catchfilebetweentags}
%\usepackage{fontspec}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{ifdraft}
\usepackage{ifthen}
%\usepackage{lualatex-math}
\usepackage{mathtools}
\usepackage{proof}
\usepackage{scalerel}
\usepackage{setspace}
\usepackage{stmaryrd}
\usepackage{supertabular}
\usepackage{tikz-cd}
%\usepackage{unicode-math}
\usepackage{url}
%\usepackage{xunicode}

@@

% fonts
%\usepackage{pxfonts}
%\usepackage{eulervm}
\usepackage[
  activate={true,nocompatibility},
  kerning=true,
  spacing=true,
  tracking=true
]{microtype}
\microtypecontext{spacing=nonfrench}
% \setmainfont{Linux Libertine O}
% \setmathfont{Asana Math}

@@

Then, fix a covariant presheaf (copresheaf) of operators
$\Of{\Operators}{\SCtx\times\Discrete{\Arities}\to\Sets}$ such that the arrows
in $\SCtx$ lift to renamings of operators' parameters. By the Grothendieck
construction $\Iso{\Grothendieck{}{\Operators}}{\Comma{*}{\Operators}}$ we have
a category of elements of $\Operators$ where objects are triples
$\Pair{\Pair{\Upsilon}{a}}{\vartheta}$, interpreted as
$\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$, and morphisms are diagrams:

\[
  \begin{tikzcd}[ampersand replacement = \&]
    \& *
      \arrow[dl, "\vartheta", swap]
      \arrow[dr, "\vartheta'"]
    \&
    \\
    {\Operators\Pair{\Upsilon}{a}}
      \arrow[rr, "\Operators\Pair{\rho}{f}", swap]
    \&
    \& {\Operators\Pair{\Upsilon'}{a'}}
    \\
    {\Pair{\Upsilon}{a}}
      \arrow[rr, "\Pair{\rho}{f}", swap]
    \&
    \& {\Pair{\Upsilon'}{a'}}
  \end{tikzcd}
\]\\

@@

Operators are defined by specifying the fibers of
$\Of{\pi_{\Operators}}{\Grothendieck{}{\Operators}\to\SCtx\times\Discrete{\Arities}}$ in
which they reside. For instance, consider the lambda calculus with a single
sort, $\SortExp$; we give its signature by asserting the following about its
operators:
\begin{gather*}
  \IsOperator{\Upsilon}{\lambda}{
    \MkArity{\MkValence{}{\SortExp}{\SortExp}}{\SortExp}
  }\\
  \IsOperator{\Upsilon}{\mathsf{ap}}{
    \MkArity{
      \MkValence{}{}{\SortExp},
      \MkValence{}{}{\SortExp}
    }{\SortExp}
  }
\end{gather*}
